---
title: "Homework 6"
author: "Lunbei Hu"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document
---

This is my solution to HW6.

```{r setup, include = FALSE}
library(tidyverse)
library(modelr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.color = "viridis",
  ggplot2.continuous.fill = "viridis"
)  

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```


## Problem 1

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```


Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

It looks like cities with larger ORs also tends to have wider confidence interval/more dispersed.

## Problem 2

```{r}
baby_df = 
  read_csv("./data/birthweight.csv") %>% 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
    ) %>% 
  mutate(
    babysex = recode(babysex, "1" = "Male", "2" = "Female"),
    frace = recode(frace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican",
                   "8" = "Other", "9" = "Unknown"),
    malform = recode(malform, "0" = "Absent", "1" = "Present"),
    mrace = recode(mrace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican",
                   "8" = "Other")
  )

sum(is.na(baby_df))
  
```

There is no missing data in the birthweight dataset.

After doing an online research, I hypothesize birthweight is associated with mother's weight at delivery, gestational age in weeks, mother's age at delivery, mother's race, average number of cigarettes smoked, so a model is fitted based on these variables.

```{r}
mod1 = lm(bwt ~ delwt + gaweeks + momage + mrace + smoken, data = baby_df)
```

```{r}
baby_df %>% 
  add_predictions(mod1) %>% 
  add_residuals(mod1) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point() +
  geom_smooth(method = "lm") + 
  labs(title = "Fitted values against residuals", 
       x = "Fitted values", 
       y = "Residuals")
```

Compare your model to two others using cross-validated prediction error.

Create a training dataset and a testing dataset.

```{r}
cv_df =
  crossv_mc(baby_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )
```

Fit my model and the other two models to the splits.

```{r}
cv_df = 
  cv_df %>% 
  mutate(
    mod1  = map(.x = train, ~lm(bwt ~ delwt + gaweeks + momage + mrace + smoken, 
                                data = .x)),
    mod2  = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    mod3  = map(.x = train, ~lm(bwt ~ bhead*blength*babysex, data = .x))
  ) %>% 
    mutate(
    rmse_mod1 = map2_dbl(.x = mod1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_mod2 = map2_dbl(.x = mod2, .y = test, ~rmse(model = .x, data = .y)),
    rmse_mod3 = map2_dbl(.x = mod3, .y = test, ~rmse(model = .x, data = .y))
    )
```

Violin plots of RMSEs

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin()
```

In terms of the cross-validated prediction error, the best model is the one using head circumference, length, sex, and all interactions - with the lowest RMSE.



